\modulechapter{mod.adminsystem.mgmt}

\generatesfrtable{mod.adminsystem.mgmt}

% \generatebundletable{mod.adminsystem.mgmt}

\moduledescription{mod.adminsystem.mgmt.desc}

The module \tds{mod.adminsystem.mgmt} of subsystem \tdslink{sub.adminsystem}
provides functionality to configure the TOE. Furthermore, the administrator can
use the module to open/close a connection to the VPN concentrator and to run the
TSF self tests.

\moduleprocesses{prc.adminsystem.mgmt}

\moduleprocess{prc.adminsystem.mgmt.setconfig}{Speichern der Konfiguration}

This process persists configuration parameters entered by the administrator via
the HTTP server.

\moduleprocess{prc.adminsystem.mgmt.connectdisconnect}{Opening and Closing the VPN Connection}

This process initiates the creation and destruction of a VPN connection. The
interface \tdslink[fq]{int.vpn.core.connect} is required for creating the
connection. The interface \tdslink[fq]{int.vpn.core.disconnect} is required for
closing the connection.

\moduleprocess{prc.adminsystem.mgmt.selftest}{Calling Self Tests}

This process initiates the self tests of module
\tdslink[fq]{mod.selfprotect.selftest}. The self tests are started by calling
\tdslink[fq]{int.selfprotect.selftest.runtest}.

\moduleinterfaces{int.adminsystem.mgmt}

\moduleinterfaceprovided{int.adminsystem.mgmt.setconfig}

This interface calls the processes for managing the configuration data of the
TOE. Configuration data can be read and written with this interface.

\moduleinterfaceprovided{int.adminsystem.mgmt.connectdisconnect}

This interface is used to initiate the opening and closing of a VPN connection
from the management interface.

\moduleinterfacerequired{int.vpn.core.connect}

The interface \tdslink[fq]{int.vpn.core.connect} is required for opening the VPN
connection.

\moduleinterfacerequired{int.vpn.core.disconnect}

The interface \tdslink[fq]{int.vpn.core.disconnect}is required for closing the
VPN connection.

\moduleinterfacerequired{int.selfprotect.selftest.runtest}

The interface is required \tdslink[fq]{int.selfprotect.selftest.runtest} for
running the self tests.






